---
title: "Homework 1 - P8105"
author: "Tim Hauser (th2899)"
date: 2022-09-23
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

The purpose of this file is to document the steps to fulfill Homework 1. 

## Problem 1

Load the Penguins dataset

```{r}
data("penguins", package = "palmerpenguins")
```

The `r nrow(penguins)` (rows) by `r ncol(penguins)` (columns) penguins dataset is a list of penguins with the following eight variables collected for each (if available): `r ls(penguins)`.

The mean flipper length across all penguins in the data set is `r round(mean(penguins$flipper_length_mm, na.rm=TRUE), 3)` mm. As a side note, in the mean calculation I ignored the NA value in row 4, because R by default returns a mean of NA if the data contains at least one NA.

Below is displayed a scatterplot with `flipper_length_mm` on the Y axis and `bill_length_mm` on the X axis, colored by `species`:

```{r yx_scatter}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

```{r}
ggsave("scatter_plot.pdf", height = 4, width = 6) 
```





First we create a dataframe containing variables for our plots.

```{r df_create}
set.seed(1234)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

First we show a histogram of the `x` variable.

```{r x_hist}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Next we show a scatterplot of `y` vs `x`. 
